\papertitle

### 2014-03-20 final-report/paper.tex

\subsubsection{Worker communication view}

The Worker Communication view consists of two charts: the aggregate communication
chart and the time series chart. The aggregate communication chart is a matrix (Figure~\ref{fig:network}) representing
a cluster of $N$ workers. Each cell $m,n$ in the matrix represents the total number of tuples sent
by worker $m$ to worker $n$ during the query execution. We chose to use the colors from color brewer\cite{harrower2003colorbrewer} and interpolated the colors between the steps using the \emph{CIE L*a*b*} interpolation and lightness correction \cite{chromajsaisch}. The colors work in grayscale and can be interpreted by color blind users.

The matrix chart representing aggregate communication between workers help uncover data skew
issues, as discussed in Section~\ref{sec:eval}.

>>>>

\subsubsection{\network view}

The \network view consists of two charts: the aggregate communication
chart and the time series chart. The aggregate communication chart is a matrix (Figure~\ref{fig:network}) representing
a cluster of $N$ workers. Each cell $m,n$ in the matrix represents the total number of tuples sent
by worker $m$ to worker $n$ during the query execution. We chose to use the colors from color brewer\cite{harrower2003colorbrewer} and interpolated the colors between the steps using the \emph{CIE L*a*b*} interpolation and lightness correction \cite{chromajsaisch}. The colors work in grayscale and can be interpreted by color blind users.

The matrix chart representing aggregate communication between workers help uncover data skew
issues, as discussed in \S \ref{sec:eval}.

We initially considered having a chord diagram\footnote{\url{http://bl.ocks.org/mbostock/4062006}} instead of a matrix
for the \network chart. But feedback during the progress presentation session convinced us that
a chord diagram would suffer from scalability problems. Adding an option for displaying a chord diagram remains
part of future work.

\todo{is this figure necessary or is the figure in the evaluation section enough?}

\begin{figure}[!ht]
  \includegraphics[width=\columnwidth]{images/networkVis1}
  \caption{\network matrix chart. Each cell represents the number of exchanged tuples between a
  pair of workers.}
  \label{fig:matrix}
\end{figure}
